Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-06-18 paper/paperv3.qmd
updating phenology n()
Updating sample sizes

@@

Sample size n = `r nrow(surv_recr_data)` observations of `r n_distinct(surv_recr_data$animalID)` individuals.

@@

>>>>

n_recruit <- surv_recr_data %>% 
  filter(pupsex == "F")

@@

Sample size for offspring survival was n = `r nrow(surv_recr_data)` observations of `r n_distinct(surv_recr_data$animalID)` individuals. Sample size for offspring recruitment was n = `r nrow(n_recruit)` observations of `r n_distinct(n_recruit$animalID)` female individuals.

@@

Sample size n = `r nrow(seal_phenology)` observations of `r n_distinct(phenology_n)` individuals.
